---
title: "Analysis of Multiple-Causes Scenario (Study 1)"
author: "Dennis and Zheng Yong"
output:
  html_document:
    df_print: paged
    number_sections: yes
    theme: readable
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: "hide"
fontsize: 18pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r loading-libraries-and-helper-functions, echo=FALSE}

# devtools::install_github("dennisteowh/dthelper")
# devtools::install_github("langcog/langcog")

library(ggplot2)
library(langcog)
library(dthelper)
library(readr)
library(tidyverse)

```

```{r loading-data, echo=FALSE}

ecl_dat <- read_csv("ecl_dat.csv")

```

# Participant Exclusion

> Number of flat responders:

```{r removing-participants-based-on-flatresp, eval = T}
# number of flat responders
sum(ecl_dat$flat)

# remove flat responders
ecl_dat <- ecl_dat[!ecl_dat$flat, ]
```

> Number of participants who failed first attention check:

```{r removing-participants-based-on-att1, eval = T}
# number of participants who failed attention1 check
sum(ecl_dat$attention1 != 2)

# remove those who failed attention1 check
ecl_dat <- ecl_dat[ecl_dat$attention1=="2",]
```

> Number of participants who failed second attention check:

```{r removing-participants-based-on-att2, eval = T}
# number who failed attention2 check
sum(!(ecl_dat$attentionOrange == 0 & ecl_dat$attentionBlue == 0 & ecl_dat$attentionBulb == 1))
pass_attention2 <- (ecl_dat$attentionOrange == 0 & ecl_dat$attentionBlue == 0 & ecl_dat$attentionBulb == 1)

# remove those who failed attention2 check
ecl_dat <- ecl_dat[pass_attention2, ]
```

> Number of outliers for total time taken:

```{r removing-participants-based-on-time, eval = T}
# outliers for Total Time taken for survey
rt_range <- 3*sd(ecl_dat$totalRT)
slow <- which(ecl_dat$totalRT > mean(ecl_dat$totalRT,na.rm = T) + rt_range)
fast <- which(ecl_dat$totalRT < mean(ecl_dat$totalRT,na.rm = T) - rt_range)

# number of outliers for Total Time taken for survey
length(slow)
length(fast)

# remove outliers
ecl_dat <- ecl_dat[-slow,]
```

> Number of participants who failed anti-bot verification:

```{r removing-participants-based-on-botCheck, eval = T}
n_fails <- which(ecl_dat$nFails > 3)
# number who failed bot check (more than 3 times)
length(n_fails)
```

> Number of remaining participants after data cleaning:

```{r participants-after-all-cleaning, eval = T}
# number of participants in each condition (after exclusions)
ecl_dat$condition <- relabel(ecl_dat$condition,
                             from = c("condition 2","condition 1"),
                             to = c("no-emotion", "emotion"))

table(ecl_dat$condition)

```

# Summary Statistics

- `relationBlue`: likelihood that blue caused bulb to light up
- `relationOrange`: likelihood that orange caused bulb to light up
- `relationOrangeBlue`: likelihood that both caused bulb to light up
- `expBlue`: likelihood that agent expected blue to cause bulb to light up
- `expOrange`: likelihood that agent expected orange to cause bulb to light up
- `expBoth`: likelihood that agent expected both to cause bulb to light up
- `desire`: likelihood that agent desired to bulb to light up
- `knowledge`: likelihood that agent knew how to turn on the bulb

```{r preparing-variables}
# normalizing desire and knowledge variables
ecl_dat$desire <- (ecl_dat$desire - 1)/8
ecl_dat$knowledge <- (ecl_dat$knowledge1 - 1)/8
```

```{r change-to-long-format}
# note these are all normalized ratings which were originally measured using Likert scales
human_cause_data <- gather.keep(ecl_dat, var.to.gather = c("relationBlueNorm", "relationOrangeNorm", "relationOrangeBlueNorm"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_expectation_data <- gather.keep(ecl_dat, var.to.gather = c("expBlueNorm", "expOrangeNorm","expBothNorm"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_desire_data <- gather.keep(ecl_dat, var.to.gather = c("desire"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_knowledge_data <- gather.keep(ecl_dat, var.to.gather = c("knowledge"), keep = c("id", "condition"), key = "structure",value="likelihood")

```

```{r compute-confidence-intervals-via-bootstrapping}
set.seed(100)

human_cause <- human_cause_data %>% group_by(condition, structure)%>%
  multi_boot_standard(col="likelihood")

human_expectation <- human_expectation_data %>% group_by(condition, structure)%>%
  multi_boot_standard(col="likelihood")

human_desire <- human_desire_data %>% group_by(condition, structure)%>%
  multi_boot_standard(col="likelihood")

human_knowledge <- human_knowledge_data %>% group_by(condition, structure)%>%
  multi_boot_standard(col="likelihood")
```


```{r histograms-of-variables, fig.height=16, fig.width=16}
library(psych)

key_variables1 <- c("relationBlueNorm", "relationOrangeNorm", "relationOrangeBlueNorm", "expBlueNorm", "expOrangeNorm","expBothNorm","desire", "knowledge")

table1 <- ecl_dat[,key_variables1] %>%
  describe()%>%
  as.data.frame()%>%
  select(n,mean,sd,median,min,max,skew,kurtosis)
knitr::kable(table1)
```

# Demographics

> Gender of participants:

```{r demographics-gender}
table(ecl_dat$gender)
```

> Proportion of females amongst participants:

```{r demographics-proportion}
table(ecl_dat$gender)[[1]]/length(ecl_dat$gender)
```

> Mean and SD for age amongst participants:

```{r demographics-age}
mean(ecl_dat$age,na.rm = T)
sd(ecl_dat$age,na.rm = T)
```

> Primary language of participants:

```{r demographics-language}
table(ecl_dat$language)
```

# Visualizing Participants' Inferences

## Causal Inferences

The bar graphs shows participants' causal inferences for:

* the hypothesis that pushing the blue box caused the bulb to light up (blue bar).
* the hypothesis that pushing the orange box caused the bulb to light up (orange bar).
* the hypothesis that pushing both boxes caused the bulb to light up (green bar).

The bar graphs on the left shows the mean likelihood ratings (normalized) of participants in the emotion condition, whereas the bar graphs on the right shows the mean likelihood ratings (normalized) of participants in the no emotion condition. Error bars represent 95% confidence intervals.

```{r causal-structure-graph,fig.width=8, fig.height=6}

human_cause$Hypothesis <- factor(human_cause$structure, labels = c("Blue Box", "Orange Box", "Both Boxes"), levels = c("relationBlueNorm", "relationOrangeNorm", "relationOrangeBlueNorm"))

human_cause$Condition <- as.numeric(relabel(human_cause$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(human_cause$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#E69F00", "#009E73")

# for future graphing purposes
plot_human_cause_left <- ggplot(human_cause, aes(x = Condition, y = mean, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_cause, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,.7) +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion","No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
   theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_human_cause <- ggplot(human_cause, aes(x = Condition, y = mean, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_cause, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,.7) +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion","No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
   #theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_human_cause
```

## Belief Inferences

The bar graphs shows participants' belief inferences for:

* the hypothesis that the agent believed that pushing the blue box would turn on the bulb (blue bar).
* the hypothesis that the agent believed that pushing the orange box would turn on the bulb (orange bar).
* the hypothesis that the agent believed that pushing both boxes would turn on the bulb (green bar).

The bar graphs on the left shows the mean likelihood ratings (normalized) of participants in the emotion condition, whereas the bar graphs on the right shows the mean likelihood ratings (normalized) of participants in the no emotion condition. Error bars represent 95% confidence intervals.

```{r expectation-graph,fig.width=8, fig.height=6}

human_expectation$Hypothesis <- factor(human_expectation$structure, labels = c("Blue Box", "Orange Box","Both Boxes"), levels = c("expBlueNorm", "expOrangeNorm","expBothNorm"))

human_expectation$Condition <- as.numeric(relabel(human_expectation$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(human_expectation$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#E69F00", "#009E73")

plot_human_expectation <- ggplot(human_expectation, aes(x = Condition, y = mean, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_expectation, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,.7) +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c("Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  ggtitle("Belief Inference")

plot_human_expectation
```


# Comparing Model Predictions to Human Data

## Correlation and Scatterplot

```{r preparing-model-predictions}

human_cause <- human_cause
human_cause$Subject <- "Human"
human_cause$labels <- c("W","W","W",
                        "W","W","W")
human_cause$key <- c("w1e","w3e","w2e",
                     "w1n","w3n","w2n")

model_cause <- data.frame(
  condition = c("emotion","emotion","emotion",
                "no-emotion","no-emotion","no-emotion"),
  Hypothesis = c("Blue Box",  "Orange Box","Both Boxes",
                "Blue Box",  "Orange Box","Both Boxes"),
  ci_lower_pred = c(0.076   , 0.405975, 0.438,
                    0.018   , 0.293975, 0.622
                    ),
  ci_upper_pred = c(0.113   , 0.466025, 0.499,
                    0.037025, 0.35    , 0.679025
                    ),
  mean_pred = c(0.0955,   0.436125, 0.468375,
                0.0275, 0.3215, 0.651
                ),
  Subject = c("Model", "Model","Model", "Model","Model", "Model"),
  labels = c("W","W","W",
             "W","W","W"),
  key = c("w1e","w2e","w3e",
          "w1n","w2n","w3n") 
)


human_expectation$Subject <- "Human"
human_expectation$labels <- c("B","B","B",
                              "B","B","B")
human_expectation$key <- c("b1e","b3e","b2e",
                           "b1n","b3n","b2n")

model_expectation <- data.frame(
  condition = c("emotion","emotion","emotion",
                "no-emotion","no-emotion","no-emotion"),
  Hypothesis = c("Blue Box", "Orange Box", "Both Boxes",
                "Blue Box", "Orange Box", "Both Boxes"),
  ci_lower_pred = c(0.391, 0.253, 0.274,
                    0.057, 0.241, 0.63
                    ),
  ci_upper_pred = c(0.449   , 0.306025, 0.328,
                    0.089, 0.298, 0.689
                    ),
  mean_pred = c(0.42,   0.2795, 0.3005,
                0.072375, 0.268625, 0.659 
                ),
  Subject = c("Model", "Model","Model", "Model","Model", "Model"),
  labels = c("B","B","B",
             "B","B","B"),
  key = c("b1e","b2e","b3e",
          "b1n","b2n","b3n")
)

human_desire$Subject <- "Human"
human_desire$labels <- c("D", "D")
human_desire$key <- c("de","dn")

model_desire <- data.frame(
  condition = c("emotion", "no-emotion"),
  ci_lower_pred = c(0.9148305084745767,0.5571428571428572),
  ci_upper_pred = c(1.0, 0.7857142857142857),
  mean_pred = c(0.96125,0.6735),
  Subject = c("Model", "Model"),
  labels = c("D", "D"),
  key = c("de","dn")
)


human_knowledge$Subject <- "Human"
human_knowledge$labels <- c("K", "K")
human_knowledge$key <- c("ke","kn")

model_knowledge <- data.frame(
  condition = c("emotion", "no-emotion"),
  ci_lower_pred = c(0.652382863412051, 0.689338574660182),
  ci_upper_pred = c(0.7343752532197032, 0.7614024391721229),
  mean_pred = c(0.6938197847847518, 0.7250887688272029),
  Subject = c("Model", "Model"),
  labels = c("K", "K"),
  key = c("ke","kn")
)


human_variable_data <- human_desire %>%
  full_join(human_expectation)%>%
  full_join(human_knowledge)%>%
  full_join(human_cause)

model_variable_data <- model_desire %>%
  full_join(model_expectation)%>%
  full_join(model_knowledge)%>%
  full_join(model_cause)

all_variable_data <- full_join(human_variable_data, model_variable_data, by = c("key","Hypothesis","labels","condition"))

all_variable_data$Condition <-factor(all_variable_data$condition,
                                     levels=c("emotion","no-emotion"),
                                     labels = c("Emotion","No Emotion"))
```

The correlation between our model's predictions on causal structure, belief, desire, and knowledge against participants' mean ratings (normalized) are shown below:
```{r computing-correlation}
cor.test(all_variable_data$mean, all_variable_data$mean_pred)
```

The scatter-plot below plots our model's predictions on causal structure, belief, desire, and knowledge against mean participants' ratings (normalized). The error bars represent 95% confidence intervals):
```{r plotting-scatterplot, fig.height=8, fig.width=8}
corplot1 <- ggplot(all_variable_data, aes(x = mean_pred, y = mean, color = Condition, shape = Condition))+
  geom_point(size=3.5) +
  geom_errorbar(data = all_variable_data, aes(x = mean_pred, ymin=ci_lower, ymax=ci_upper), width = .04, size = .4)+
  geom_errorbarh(data = all_variable_data, aes(y = mean, xmin=ci_lower_pred, xmax=ci_upper_pred), height = .04, size = .4)+
  geom_abline(intercept = 0, slope = 1,linetype = 2) +
  xlim(0, 1.05) +
  ylim(0,1.05)+
  coord_fixed(ratio = 1)+
  ylab("Human Ratings")+
  xlab("Model Predictions")+
  #geom_text(aes(label = paste0(labels)), nudge_x = 0.02, nudge_y = 0.02, show.legend = FALSE, size =4) +
  ggtitle("Multiple-Causes (Study 1)")+
  theme_bw()+
    theme(text = element_text(size = 20),
        plot.title = element_text(face = "bold", size = 20, hjust = 0.5)) +
  annotate("text", x=.25, y=.6, label= "r = .88", size = 6) 

corplot1
```

## Bar Graphs Comparing Causal and Belief Inferences

The bar graphs below compares our model's predictions on causal and belief inference against mean participants' ratings (normalized). The error bars represent 95% confidence intervals. Participants' ratings are shown on the top row of bar graphs, whereas our model's predictions are illustrated on the bottom row.
```{r causal-structure-graph-model}

model_cause$Hypothesis <- factor(model_cause$Hypothesis, labels = c("Blue Box", "Orange Box", "Both Boxes"), levels = c("Blue Box", "Orange Box", "Both Boxes"))

model_cause$Condition <- as.numeric(relabel(model_cause$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(model_cause$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#E69F00", "#009E73")

# for future graphing purposes
plot_model_cause_left <- ggplot(model_cause, aes(x = Condition, y = mean_pred, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_cause, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion","No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
   theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_model_cause <- ggplot(model_cause, aes(x = Condition, y = mean_pred, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_cause, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,.7) +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion","No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
   #theme(legend.position="none") +
  ggtitle("Causal Inference")

```

```{r expectation-graph-model}

model_expectation$Hypothesis <- factor(model_expectation$Hypothesis, labels = c("Blue Box", "Orange Box","Both Boxes"), levels = c("Blue Box", "Orange Box","Both Boxes"))

model_expectation$Condition <- as.numeric(relabel(model_expectation$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(model_expectation$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#E69F00", "#009E73")

plot_model_expectation <- ggplot(model_expectation, aes(x = Condition, y = mean_pred, fill = Hypothesis)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_expectation, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Hypothesis), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,.7) +
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c("Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  ggtitle("Belief Inference")

```

```{r causal-belief-side-by-side-plot, fig.width=18, fig.height=14}
# plotting causal inference and belief inference side by side

library(grid)
grid.newpage()
grid.draw(rbind(cbind(ggplotGrob(plot_human_cause_left), ggplotGrob(plot_human_expectation), size = "last"),
          cbind(ggplotGrob(plot_model_cause_left), ggplotGrob(plot_model_expectation), size = "last")))
#500 x 1000

```

# Hypothesis Testing

## Causal Inferences

Participants in the emotion condition were less likely to infer that the blue box turned on the bulb ($t(127) = -3.33, p = .001$), than participants in the no-emotion condition. This is consistent with our postulation (See General Discussion of main paper) that participants in the no emotion condition were less likely to discount the "blue box" hypothesis as they were less motivated to explain the absence of an outcome compared to the participants in the emotion condition who were motivated to explain the agent's failure.
```{r testing-hypotheses-on-causal-structure-blue}
t.test(relationBlue ~ condition, ecl_dat)
```

As expected, participants in the emotion condition were more likely to infer that the orange box turned on the bulb ($t(120.63) = 3.06, p = .003$), than participants in the no-emotion condition. We explained that participants in the emotion condition saw the agent's first action (pushing blue box) as a mistake and hence, gave higher likelihood to the other box (orange box).
```{r testing-hypotheses-on-causal-structure-orange}
t.test(relationOrange ~ condition, ecl_dat)
```

Also, participants in the emotion condition were less likely to infer that pushing both boxes turned on the bulb ($t(100.42) = -3.51, p = .007$), than participants in the no-emotion condition. We explained that participants in the no-emotion condition assumed that both of the agent's actions were intended and hence, inferred through the agent's knowledge that both boxes were causally important to turn on the bulb.
```{r testing-hypotheses-on-causal-structure-both}
t.test(relationOrangeBlue ~ condition, ecl_dat)

```

## Belief Inferences

On belief inference, participants in the emotion condition were more likely to infer that the agent expected the blue box to turn on the bulb ($t(125.76) = 5.09, p < .001$) than participants in the no-emotion condition. This is consistent with our interpretation that participants in the emotion condition inferred that the agent expected that pushing the blue box would turn on the bulb, hence leading to his initial failed action.
```{r testing-hypotheses-on-expectation-blue}
t.test(expBlue ~ condition, ecl_dat)
```

Both conditions did not statistically differ on their inference of the agent's belief in the orange box as a causal antecedent.

```{r testing-hypotheses-on-expectation-orange}
t.test(expOrange ~ condition, ecl_dat)
```

Participants in the emotion condition were less likely to infer that the agent expected both boxes to turn on the bulb ($t(116.91) = -3.56, p < 0.001$) than participants in the no-emotion condition. Again, this is consistent with the interpretation that the participants inferred the agent's intention to push box boxes from the beginning.

```{r testing-hypotheses-on-expectation-both}
t.test(expBoth ~ condition, ecl_dat)

```

## Desire Inferences

With regards to desire inference, it did not statistically differ across conditions. From the means, we can see that participants in both conditions inferred that the agent likely desired to turn on the bulb.
```{r testing-desire-inferences}
t.test(desire ~ condition, ecl_dat)
```

These ratings describe the non-normalized desire ratings collected on a Likert scale (from 1 to 9).
```{r descriptives-for-desire-inferences}
ecl_dat %>%
  group_by(condition) %>%
  summarise(
    desire = paste0(round(mean(desire, na.rm = T),2)," (",round(sd(desire, na.rm = T),2), ")")
  )
```


## Knowledge Inferences

Finally, with regards to knowledge inference, participants in the emotion condition were less likely to infer that the agent was knowledgeable about how to turn on the bulb ($t(116.43) = -5.33, p < .001$) than participants in the no-emotion condition. This makes sense as the agent in the emotion condition signalled that he failed his initial action (pushing the blue box).
```{r testing-knowledge-inferences}
t.test(knowledge1 ~ condition, ecl_dat)
```
These ratings describe the non-normalized knowledge ratings collected on a Likert scale (from 1 to 9).
```{r descriptives-for-knowledge-inferences}
ecl_dat %>%
  group_by(condition) %>%
  summarise(
    knowledge = paste0(round(mean(knowledge1, na.rm = T),2)," (",round(sd(knowledge1, na.rm = T),2), ")")
  )
```