---
title: "Analysis of Multiple-Outcomes Scenario (Study 2)"
author: "Dennis and Zheng Yong"
output:
  html_document:
    df_print: paged
    number_sections: yes
    theme: readable
    highlight: tango
    toc: yes
    toc_depth: 3
    code_folding: "hide"
fontsize: 16pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r loading-libraries-and-helper-functions, echo= F}

# devtools::install_github("dennisteowh/dthelper")
# devtools::install_github("langcog/langcog")

library(ggplot2)
library(langcog)
library(dthelper)
library(readr)
library(tidyverse)

```

```{r loading-data, echo=FALSE}
# setwd("~/Dropbox/8 and above/Emotions and Causal Learning/Analysis/cog-sci-present/multiple-outcomes-scenario")

ecl_dat <- read_csv("../clean data/ecl_dat.csv")
```

# Participant Exclusion

> Number of flat responders:

```{r removing-participants-based-on-criteria, eval = T}
# number of flat responders
sum(ecl_dat$flat)

# remove flat responders
ecl_dat <- ecl_dat[!ecl_dat$flat, ]
```

> Number of participants who failed first attention check:

```{r removing-participants-based-on-att1, eval = T}
# number of px who failed attention1
sum(ecl_dat$attention1 != 2)

# remove those who failed attention1 check
ecl_dat <- ecl_dat[ecl_dat$attention1=="2",]
```

> Number of participants who failed second attention check:

```{r removing-participants-based-on-att2, eval = T}
# number who failed attention2 check
sum(!(ecl_dat$attentionBulb1 == 0 & ecl_dat$attentionBulb2 == 1) )
pass_attention2 <- (ecl_dat$attentionBulb1 == 0 & ecl_dat$attentionBulb2 == 1)

# remove those who failed attention2 check
ecl_dat <- ecl_dat[pass_attention2, ]
```

> Number of outliers for total time taken:

```{r removing-participants-based-on-time, eval = T}
# outlier for total time taken to complete survey
rt_range <- 3*sd(ecl_dat$totalRT)
slow <- which(ecl_dat$totalRT > mean(ecl_dat$totalRT,na.rm = T) + rt_range)
fast <- which(ecl_dat$totalRT < mean(ecl_dat$totalRT,na.rm = T) - rt_range)

# number of outliers
length(slow)
length(fast)

# remove outliers
ecl_dat <- ecl_dat[-slow,]
```

> Number of participants who failed anti-bot verification:

```{r removing-participants-based-on-botCheck, eval = T}
n_fails <- which(ecl_dat$nFails > 3)
# number who failed bot check (more than 3 times)
length(n_fails)
```

> Number of remaining participants after data cleaning:

```{r participants-after-all-cleaning, eval = T}
# number of participants in each condition (after exclusions)
ecl_dat$condition <- relabel(ecl_dat$condition,
                             from = c("condition 1", "condition 2"),
                             to = c("emotion", "no-emotion"))
table(ecl_dat$condition)

```

# Summary Statistics

```{r preparing-variables}

ecl_dat$relationBlueOneNorm <- (ecl_dat$relationBlueOne - 1)/8
ecl_dat$relationBlueTwoNorm <- (ecl_dat$relationBlueTwo - 1)/8
ecl_dat$exp1Norm <- (ecl_dat$exp1 - 1)/8
ecl_dat$exp2Norm <- (ecl_dat$exp2 - 1)/8
ecl_dat$desire1Norm <- (ecl_dat$desire1 - 1)/8
ecl_dat$desire2Norm <- (ecl_dat$desire2 - 1)/8
ecl_dat$knowledgeNorm <- (ecl_dat$knowledge1 - 1)/8

#write.csv(ecl_dat, file = "ecl_dat_multiple-outcome.csv")
```


```{r change-to-long-format}

human_cause_data <- gather.keep(ecl_dat, var.to.gather = c("relationBlueOneNorm", "relationBlueTwoNorm"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_expectation_data <- gather.keep(ecl_dat, var.to.gather = c("exp1Norm","exp2Norm"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_desire_data <- gather.keep(ecl_dat, var.to.gather = c("desire1Norm", "desire2Norm"), keep = c("id", "condition"), key = "structure",value="likelihood")

human_knowledge_data <- gather.keep(ecl_dat, var.to.gather = c("knowledgeNorm"), keep = c("id", "condition"), key = "structure",value="likelihood")
```


```{r compute-confidence-intervals-via-bootstrapping}
set.seed(100)

human_cause <- human_cause_data %>% group_by(condition, structure) %>%
  multi_boot_standard(col="likelihood")

human_expectation <- human_expectation_data %>% group_by(condition, structure) %>%
  multi_boot_standard(col="likelihood")

human_desire <- human_desire_data %>% group_by(condition, structure) %>%
  multi_boot_standard(col="likelihood")

human_knowledge <- human_knowledge_data %>% group_by(condition, structure) %>%
  multi_boot_standard(col="likelihood")

```

```{r histograms-of-variables, fig.height=16, fig.width=16}
library(psych)

key_variables1 <- c("relationBlueOneNorm", "relationBlueTwoNorm", "exp1Norm", "exp2Norm", "desire1Norm", "desire2Norm","knowledgeNorm" )

table1 <- ecl_dat[,key_variables1] %>%
  describe()%>%
  as.data.frame()%>%
  select(n,mean,sd,median,min,max,skew,kurtosis)
knitr::kable(table1)

# relationOneTwo: likelihood of causal relationship between bulb 1 and bulb 2
# relationBlueTwo: likelihood of causal relationship between box and bulb 1
# relationBlueTwo: likelihood of causal relationship between box and bulb 2
# expButton: expects that box lights up
# exp1: expects that bulb 1 lights up
# exp2: expects that bulb 2 lights up
```

# Demographics

> Gender of participants:

```{r demographics}
table(ecl_dat$gender)
```

> Proportion of females amongst participants:

```{r demographics-proportion}
table(ecl_dat$gender)[[1]]/length(ecl_dat$gender) # prop females
```

> Mean and SD for age amongst participants:

```{r demographics-age}
mean(ecl_dat$age,na.rm = T)
sd(ecl_dat$age,na.rm = T)
```

> Primary language of participants:

```{r demographics-language}
table(ecl_dat$language)
```

# Visualizing Participants' Inferences

## Causal Inferences

The bar graphs shows participants' causal inferences for:

* (blue bar) pushing the box causes the purple bulb to light up.
* (orange bar) pushing the box causes the red bulb to light up.

The bar graphs on the left shows the likelihood ratings of participants in the emotion (experimental) condition, whereas the bar graphs on the right shows the likelihood ratings of participants in the no emotion (control) condition.

```{r causal-structure-graph,fig.width=8, fig.height=6}

human_cause$Structure <- factor(human_cause$structure, labels = c("Box and Purple Bulb","Box and Red Bulb"), levels = c("relationBlueOneNorm", "relationBlueTwoNorm"))

human_cause$Condition <- as.numeric(relabel(human_cause$condition,
                                   from = c("emotion", "no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(human_cause$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c( "#0072B2", "#D55E00","#009E73")

plot_human_cause_left <- ggplot(human_cause, aes(x = Condition, y = mean, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_cause, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,1)+
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_human_cause <- ggplot(human_cause, aes(x = Condition, y = mean, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_cause, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,1)+
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  #theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_human_cause
```


## Belief Inferences

The bar graphs shows participants' belief inferences for:

* (blue bar) the agent believing that pushing the box causes the purple bulb to light up.
* (orange bar) the agent believing that pushing the box causes the red bulb to light up.

The bar graphs on the left shows the likelihood ratings of participants in the emotion (experimental) condition, whereas the bar graphs on the right shows the likelihood ratings of participants in the no emotion (control) condition.
```{r expectation-graph,fig.width=8, fig.height=6}

human_expectation$Structure <- factor(human_expectation$structure, labels = c("Purple Bulb", "Red Bulb"), levels = c("exp1Norm","exp2Norm"))

human_expectation$Condition <- as.numeric(relabel(human_expectation$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(human_expectation$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#D55E00", "#009E73")

plot_human_expectation <- ggplot(human_expectation, aes(x = Condition, y = mean, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = human_expectation, aes(x = Condition,ymin=ci_lower, ymax=ci_upper, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,1)+
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c("Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  ggtitle("Belief Inference")

plot_human_expectation
```

# Comparing Model Predictions to Human Data

## Correlation and Scatterplot

```{r preparing-model-predictions}
human_desire$Subject <- "Human"
human_desire$labels <- c("D", "D","D", "D")
human_desire$key <- c("d1e","d2e","d1n","d2n")

model_desire <- data.frame(
  condition = c("emotion", "emotion", "no-emotion","no-emotion"),
  Structure = c("Purple Bulb", "Red Bulb", "Purple Bulb", "Red Bulb"),
  ci_lower_pred = c(0.9195, 0.0405, 
                    0.2034875, 0.7164875),
  ci_upper_pred = c(0.9765, 0.0645, 
                    0.2655, 0.780525),
  mean_pred = c( 0.9483125, 0.0516875, 
                 0.2343125, 0.7469375
                 ),
  Subject = c("Model", "Model","Model", "Model"),
  labels = c("D", "D","D", "D"),
  key = c("d1e","d2e","d1n","d2n")
)

human_expectation <- human_expectation
human_expectation$Subject <- "Human"
human_expectation$labels <- c("B","B","B","B")
human_expectation$key <- c("b1e","b2e","b1n","b2n")

model_expectation <- data.frame(
  condition = c("emotion","emotion","no-emotion","no-emotion"),
  Structure = c("Purple Bulb", "Red Bulb", "Purple Bulb", "Red Bulb"),
  ci_lower_pred = c(0.8827354270268029,0.48780842200607044,
                    0.19336573419088857,0.7999782127405128
                    ),
  ci_upper_pred = c(0.9467683325793091,0.6938234913162087,
                    0.3930769737526257,0.9399937244146536
                    ),
  mean_pred = c(0.9169787468930777,0.5914374148151671,
                0.29162905960270086, 0.8785007239421384
                ),
  Subject = c("Model", "Model","Model", "Model"),
  labels = c("B","B","B","B"),
  key = c("b1e","b2e","b1n","b2n")
)

human_knowledge$Subject <- "Human"
human_knowledge$labels <- c("K", "K")
human_knowledge$key <- c("ke","kn")

model_knowledge <- data.frame(
  condition = c("emotion", "no-emotion"),
  ci_lower_pred = c(0.6046379468896996,0.673375162642256),
  ci_upper_pred = c(0.684843689631173, 0.7542611779781163),
  mean_pred = c(0.6438598614053981,0.7140678680064141),
  Subject = c("Model", "Model"),
  labels = c("K", "K"),
  key = c("ke","kn")
)

human_cause <- human_cause
human_cause$Subject <- "Human"
human_cause$labels <- c("W","W","W","W")
human_cause$key <- c("w1e","w2e","w1n","w2n")

model_cause <- data.frame(
  condition = c("emotion","emotion","no-emotion","no-emotion"),
  Structure = c("Box and Purple Bulb", "Box and Red Bulb", "Box and Purple Bulb", "Box and Red Bulb"),
  ci_lower_pred = c(0.11748851925940453,0.8703572237077039,
                    0.06115659864161587,0.8923007154207211
                    ),
  ci_upper_pred = c(0.24865624970756112,0.9596766221292115,
                    0.1720956233790888,0.9714265861532441
                    ),
  mean_pred = c(0.1803415186334381,0.9178098797982986,
                0.11316700544941195,0.9343713681513062
                ),
  Subject = c("Model", "Model","Model", "Model"),
  labels = c("W","W","W","W"),
  key = c("w1e","w2e","w1n","w2n") 
)

human_variable_data <- human_desire %>%
  full_join(human_expectation)%>%
  full_join(human_knowledge)%>%
  full_join(human_cause)

model_variable_data <- model_desire %>%
  full_join(model_expectation)%>%
  full_join(model_knowledge)%>%
  full_join(model_cause)

all_variable_data <- full_join(human_variable_data, model_variable_data, by = c("key","Structure","labels","condition"))

all_variable_data$Condition <-factor(all_variable_data$condition,
                                     levels=c("emotion","no-emotion"),
                                     labels = c("Emotion","No Emotion"))
```

The correlation between our model's predictions (normalized) on causal structure, belief, desire, and knowledge against participants' ratings (normalized) are shown below:
```{r computing-correlation}
cor.test(all_variable_data$mean, all_variable_data$mean_pred)
```

The scatterplot below shows our model's predictions (normalized) on causal structure, belief, desire, and knowledge against participants' ratings (normalized):
```{r plotting-scatterplot, fig.height=8, fig.width=8}
corplot2 <- ggplot(all_variable_data, aes(x = mean_pred, y = mean, color = Condition, shape = Condition))+
  geom_point(size=3.5) +
  geom_errorbar(data = all_variable_data, aes(x = mean_pred, ymin=ci_lower, ymax=ci_upper), width = .04, size = .4)+
  geom_errorbarh(data = all_variable_data, aes(y = mean, xmin=ci_lower_pred, xmax=ci_upper_pred), height = .04, size = .4)+
  geom_abline(intercept = 0, slope = 1,linetype = 2) +
  xlim(0, 1.05) +
  ylim(0,1.05)+
  coord_fixed(ratio = 1)+
  ylab("Human Ratings")+
  xlab("Model Predictions")+
  #geom_text(aes(label = paste0(labels)), nudge_x = -0.02, nudge_y = 0.02, show.legend = FALSE, size =4) +
  ggtitle("Multiple-Outcomes (Study 2)")+
  theme_bw()+
    theme(text = element_text(size = 20),
        plot.title = element_text(face = "bold", size = 20, hjust = 0.5)) +
  annotate("text", x=.25, y=.6, label= "r = .92", size = 6) 

corplot2
```

## Barplots Comparing Causal and Belief Inferences

The barplots below compares our model's predictions (normalized) on causal and belief inference against participants' ratings (normalized). Participants' ratings are shown as the top row of barplots, whereas our model's predictions are illustrated on the bottom row.
```{r causal-structure-graph-model}

model_cause$Structure <- factor(model_cause$Structure, labels = c("Box and Purple Bulb","Box and Red Bulb"), levels = c("Box and Purple Bulb","Box and Red Bulb"))

model_cause$Condition <- as.numeric(relabel(model_cause$condition,
                                   from = c("emotion", "no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(model_cause$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c( "#0072B2", "#D55E00","#009E73")

plot_model_cause_left <- ggplot(model_cause, aes(x = Condition, y = mean_pred, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_cause, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  theme_bw() + xlab("")+
  ylim(0,1)+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  theme(legend.position="none") +
  ggtitle("Causal Inference")

plot_model_cause <- ggplot(model_cause, aes(x = Condition, y = mean_pred, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_cause, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,1)+
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c( "Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 24),
        axis.text.x = element_text(face = "bold", size = 24, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 24, hjust = 0.5))  +
  #theme(legend.position="none") +
  ggtitle("Causal Inference")

```

```{r expectation-graph-model}


model_expectation$Structure <- factor(model_expectation$Structure, labels = c("Purple Bulb", "Red Bulb"), levels = c("Purple Bulb", "Red Bulb"))

model_expectation$Condition <- as.numeric(relabel(model_expectation$condition,
                                   from = c("emotion","no-emotion"),
                                   to = rev(c(1,2))
                                   ))

breaks <- unique(model_expectation$Condition)

#999999 - grey
#E69F00 - orange
#56B4E9 - light blue
#009E73 - green
#F0E442 - yellow
#0072B2 - dark blue
#D55E00 - red
#CC79A7 - pink

colorBlindGrey3   <- c("#0072B2", "#D55E00", "#009E73")

plot_model_expectation <- ggplot(model_expectation, aes(x = Condition, y = mean_pred, fill = Structure)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar( data = model_expectation, aes(x = Condition,ymin=ci_lower_pred, ymax=ci_upper_pred, fill= Structure), position=position_dodge(.9), width = .5, size = .5)+
  ylab("Likelihood Ratings")  +
  ylim(0,1)+
  theme_bw() + xlab("")+
  scale_x_reverse(breaks=breaks, labels=c("Emotion", "No Emotion")) +
  scale_fill_manual(values = colorBlindGrey3) +
  theme(text = element_text(size = 22),
        axis.text.x = element_text(face = "bold", size = 22, hjust = 0.5),
        plot.title = element_text(face = "bold", size = 22, hjust = 0.5))  +
  ggtitle("Belief Inference")

```

```{r causal-belief-side-by-side-plot, fig.width=18, fig.height=14}
library(grid)
grid.newpage()
grid.draw(rbind(cbind(ggplotGrob(plot_human_cause_left), ggplotGrob(plot_human_expectation), size = "last"),
          cbind(ggplotGrob(plot_model_cause_left), ggplotGrob(plot_model_expectation), size = "last")))
#1300x800
```


# Hypothesis Testing

## Causal Inferences

_t_-tests were performed to determine whether the differences between the means of participants' causal inferences were significant across the conditions.

On causal inference, participants' ratings that the box turns on the purple bulb did not statistically differ across conditions.
```{r testing-hypotheses-on-causal-structure-purple}
t.test(relationBlueOne ~ condition, ecl_dat)
```

Participants' ratings that the box turns on the red bulb also did not statistically differ across conditions.
```{r testing-hypotheses-on-causal-structure-red}
t.test(relationBlueTwo ~ condition, ecl_dat)

```

## Belief Inferences

_t_-tests were also performed to determine whether the differences between the means of participants' belief inferences were significant across the conditions.

On belief inference, participants in the emotion condition were more likely to infer that the agent expected the box to turn on the purple bulb ($t(119.57) = 8.68, p < .001$) than participants in the no-emotion condition.
```{r testing-hypotheses-on-expectation-purple}
t.test(exp1 ~ condition, ecl_dat)
```

Additionally, participants in the emotion condition were less likely to infer that the agent expected the box to turn on the red bulb ($t(117.95) = -11.05, p < .001$) than participants in the no-emotion condition.
```{r testing-hypotheses-on-expectation-red}
t.test(exp2 ~ condition, ecl_dat)

```

## Desire Inferences

_t_-tests were also performed to determine whether the differences between the means of participants' desire inferences were significant across the conditions.

On desire inference, participants in the emotion condition were more likely to infer that the agent desired the purple bulb to be switched on ($t(117.28) = 8.13, p < .001$) than participants in the no-emotion condition.
```{r testing-desire-purple}
t.test(desire1 ~ condition, ecl_dat) # bulb1
```

On the other hand, participants in the emotion condition were less likely to infer that the agent desired the purple bulb to be switched on ($t(116.78) = -10.40, p < .001$) than participants in the no-emotion condition.
```{r testing-desire-red}
t.test(desire2 ~ condition, ecl_dat) # bulb2

```

```{r descriptives-for-desire-inferences}
ecl_dat %>%
  group_by(condition) %>%
  summarise(
    desirePurple = paste0(round(mean(desire1, na.rm = T),2)," (",round(sd(desire1, na.rm = T),2), ")"),
    desireRed = paste0(round(mean(desire2, na.rm = T),2)," (",round(sd(desire2, na.rm = T),2), ")")
  )
```

## Knowledge Inferences
Finally, with regards to knowledge inference, participants in the emotion condition were less likely to infer that the agent was knowledgeable about what pushing the box results in ($t(122.85) = -2.46, p = 0.02$) than participants in the no-emotion condition.

```{r testing-knowledgability}
t.test(knowledge1 ~ condition, ecl_dat)
```

```{r descriptives-for-knowledge-inferences}
ecl_dat %>%
  group_by(condition) %>%
  summarise(
    knowledge1 = paste0(round(mean(knowledge1, na.rm = T),2)," (",round(sd(knowledge1, na.rm = T),2), ")")
  )
```
